%====================
% EXPERIENCE A
%====================
\subsection{{Data Scientist @ AUNA \hfill Dec, 2021 --- Present}}
\subtext{Retail Pharmacy Department}
\begin{zitemize}
\item Saved over S/36k per month after the execution of a proposal of warehouses redistribution and a coverage optimization using geoanalysis with Python and Kepler.gl.
\item Developed a customer segmentation model and deployed an automated pipeline (integration of Python, AWS Lambda and GitHub Actions with Serverless framework).
\item Designed and analyzed multiple AB tests for product features and marketing strategies. \item Developed a transactional forecast model for budgeting.
\item Developed an association rules model for designing promotional strategies.
\item Automated processes with Python and AWS Lambda for monitoring and measuring the impact of changes in delivery pricing.
\item Responsible for the development of data-driven strategies across multiple business areas (operations, marketing and product).
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Data Analyst SSr @ PedidosYa (Delivery Hero) \hfill Sep, 2021 --- Dec, 2021}}
\subtext{Logistics \& Operations Department}
\begin{zitemize}
\item Responsible for the analysis of performance of operations in the southern cities of Peru.
\item Responsible for the demand forecast monitoring to improve the operational efficiency.
\item Responsible for the expansion opportunity assessment using geoanalysis techniques with Python and Kepler.gl.
\item Responsible for monitoring the coverage optimization algorithm.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Business Intelligence Analyst @ PedidosYa (Delivery Hero) \hfill May, 2021 --- Sep, 2021}}
\subtext{Marketing \& Strategy Department}
\begin{zitemize}
\item Responsible for the analysis and development of strategies in the main business vertical  (83\% of its monthly revenue), which had a continuous growth of 7\% per month.
\item Responsible for designing, developing, deploying and automating multiple dashboards using DataStudio and BigQuery for daily, weekly and monthly business reviews.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Pricing Analytics Intern @ Banco de Crédito del Perú \hfill Jan, 2021 --- May, 2021}}
\subtext{Pricing \& Analytics Department}
\begin{zitemize}
\item Part of the team that developed the FX project (foreign exchange market) for the prediction of customer's closing quotation price.
\item Developed a customer segmentation analysis using classification trees for financial products portfolio management.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{Lending Strategy Intern @ Interbank \hfill Jan, 2020 --- Dec, 2020}}
\subtext{Commercial Banking Department}
\begin{zitemize}
\item Designed and developed a desktop application in C\# for the management of special commissions for corporate customers.
\item Responsible for automation of data extraction, transformation and loading (ETL) processes with SQL Server Integration Services.
\item Responsible for market analysis of financial products and services (Foreign Trade and Financing Sales).
\end{zitemize}
